Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Experiments
Work in progress

\begin{table}[]
    \scriptsize
    \centering
    \caption{Bohachevsky Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_bohachevsky5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Bohachevsky - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.28E-08 & 2.20E-08 & 15,010 & 24.2 \\
    \textbf{Elite Projection} & 4.51E-08 & 2.94E-08 & 8,266 & 12.6 \\
    \textbf{All Random} & 6.16E-08 & 2.85E-08 & 11,998 & 21.7 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Bohachevsky Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_bohachevsky10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Bohachevsky - 10   Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.66E-08 & 1.38E-08 & 40,166 & 44.4 \\
    \textbf{Elite Projection} & 3.80E-08 & 3.34E-08 & 8,506 & 12.9 \\
    \textbf{All Random} & 5.34E-08 & 3.76E-08 & 19,537 & 26.8 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

\begin{table}[]
    \scriptsize
    \centering
    \caption{Griewank Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_griewank5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Griewank - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 6.92E-08 & 2.40E-08 & 44,566 & 48.3 \\
    \textbf{Elite Projection} & 3.77E-08 & 2.74E-08 & 16,412 & 20.1 \\
    \textbf{All Random} & 5.63E-08 & 2.99E-08 & 35,761 & 38.5 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Griewank Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_griewank10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Griewank - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.07E-08 & 1.39E-08 & 92,885 & 100.0 \\
    \textbf{Elite Projection} & 4.21E-08 & 3.40E-08 & 13,534 & 17.3 \\
    \textbf{All Random} & 5.08E-08 & 3.54E-08 & 40,544 & 52.5 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

\begin{table}[]
    \scriptsize
    \centering
    \caption{Rastrigin Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rastrigin5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Rastrigin - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.85E-08 & 1.59E-08 & 22,322 & 34.1 \\
    \textbf{Elite Projection} & 4.42E-08 & 3.26E-08 & 10,860 & 14.8 \\
    \textbf{All Random} & 5.66E-08 & 2.81E-08 & 21,122 & 35.0 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Rastrigin Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rastrigin10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Rastrigin - 10   Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.56E-08 & 1.23E-08 & 53,579 & 58.7 \\
    \textbf{Elite Projection} & 3.17E-08 & 2.57E-08 & 8,704 & 13.0 \\
    \textbf{All Random} & 5.00E-08 & 3.16E-08 & 24,376 & 27.4 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

\begin{table}[]
    \scriptsize
    \centering
    \caption{Sphere Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_sphere5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Sphere - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.82E-08 & 1.65E-08 & 11,312 & 14.5 \\
    \textbf{Elite Projection} & 3.60E-08 & 3.27E-08 & 7,056 & 10.9 \\
    \textbf{All Random} & 6.14E-08 & 2.79E-08 & 9,158 & 12.2 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Sphere Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_sphere10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Sphere - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.39E-08 & 1.45E-08 & 30,769 & 34.4 \\
    \textbf{Elite Projection} & 4.28E-08 & 3.06E-08 & 9,236 & 13.3 \\
    \textbf{All Random} & 5.32E-08 & 3.38E-08 & 21,465 & 26.3 \\ \bottomrule
    \end{tabular}
    \end{table}

>>>>

\begin{table}[]
    \scriptsize
    \centering
    \caption{Bohachevsky Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_bohachevsky5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Bohachevsky Function - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.28E-08 & 2.20E-08 & 15,010 & 24.2 \\
    \textbf{Elite Projection} & 4.51E-08 & 2.94E-08 & 8,266 & 12.6 \\
    \textbf{All Random} & 6.16E-08 & 2.85E-08 & 11,998 & 21.7 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Bohachevsky Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_bohachevsky10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Bohachevsky Function - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.66E-08 & 1.38E-08 & 40,166 & 44.4 \\
    \textbf{Elite Projection} & 3.80E-08 & 3.34E-08 & 8,506 & 12.9 \\
    \textbf{All Random} & 5.34E-08 & 3.76E-08 & 19,537 & 26.8 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

\begin{table}[]
    \scriptsize
    \centering
    \caption{Griewank Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_griewank5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Griewank Function - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 6.92E-08 & 2.40E-08 & 44,566 & 48.3 \\
    \textbf{Elite Projection} & 3.77E-08 & 2.74E-08 & 16,412 & 20.1 \\
    \textbf{All Random} & 5.63E-08 & 2.99E-08 & 35,761 & 38.5 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Griewank Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_griewank10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Griewank Function - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.07E-08 & 1.39E-08 & 92,885 & 100.0 \\
    \textbf{Elite Projection} & 4.21E-08 & 3.40E-08 & 13,534 & 17.3 \\
    \textbf{All Random} & 5.08E-08 & 3.54E-08 & 40,544 & 52.5 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

\begin{table}[]
    \scriptsize
    \centering
    \caption{Rastrigin Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rastrigin5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Rastrigin Function - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.85E-08 & 1.59E-08 & 22,322 & 34.1 \\
    \textbf{Elite Projection} & 4.42E-08 & 3.26E-08 & 10,860 & 14.8 \\
    \textbf{All Random} & 5.66E-08 & 2.81E-08 & 21,122 & 35.0 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Rastrigin Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rastrigin10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Rastrigin Function - 10   Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.56E-08 & 1.23E-08 & 53,579 & 58.7 \\
    \textbf{Elite Projection} & 3.17E-08 & 2.57E-08 & 8,704 & 13.0 \\
    \textbf{All Random} & 5.00E-08 & 3.16E-08 & 24,376 & 27.4 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

\begin{table}[]
    \scriptsize
    \centering
    \caption{Sphere Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_sphere5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Sphere Function - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.82E-08 & 1.65E-08 & 11,312 & 14.5 \\
    \textbf{Elite Projection} & 3.60E-08 & 3.27E-08 & 7,056 & 10.9 \\
    \textbf{All Random} & 6.14E-08 & 2.79E-08 & 9,158 & 12.2 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Sphere Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_sphere10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Sphere Function - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.39E-08 & 1.45E-08 & 30,769 & 34.4 \\
    \textbf{Elite Projection} & 4.28E-08 & 3.06E-08 & 9,236 & 13.3 \\
    \textbf{All Random} & 5.32E-08 & 3.38E-08 & 21,465 & 26.3 \\ \bottomrule
    \end{tabular}
    \end{table}
